On the discovery and origin of $r$-process stars in the Milky Way

### 2018-02-28 article/ms.tex
minor

	\begin{abstract}
		The production of heavy elements occurs through the slow and rapid neutron capture process. Numerous sites satisfy the conditions needed for the r-process but the relative frequency of these sites is unknown, largely due to the lack of a large number of stars with strong r-process signatures. Here we report the discovery of 47 r-process enhanced stars discovered in the second LAMOST data release (DR2), more than doubling the known number in the Galaxy. Taking expected rates of core-collapse supernovae and the average r-process material ejected per event, we find that core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work within the lifetime of the universe. Current estimates of neutron-star merger rates imply that there should be about 13,000 r-process enhanced stars in the Milky Way, and about $79$ in LAMOST DR2. We find that neutron-star mergers are able to create all currently known r-process enhanced stars within $10.57 \times 10^{9}$ years. To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way. All 47 r-process enhanced stars have $[{\rm Fe/H}] > -2$, providing the first evidence against the hypothesis that r-process signatures are only found in poor metallicity environments.
	\end{abstract}

@@

    By using the assumptions listed, neutron-star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.87\times10^{9}$ years, very close to the age of the universe. From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $2.4\times10^{11}$ years, orders of magnitude longer than the age of the universe. This illustrates, with our current knowledge of core-collapse supernovae frequency, and the amount of r-process material they eject, that core-collapse supernovae cannot be the sole source of r-process enrichment in the Milky Way.

    This is reinforced by the r-process enhanced stars found in the LAMOST sample. Our 47 stars represent almost 10\% of all enhanced stars present in the Milky Way if core-collapse supernovae is considered to be the singular source of r-process enhanced stars. However, the LAMOST data release 2 only surveyed 0.00088\% of the Milky Way. It is highly unlikely that close to 10\% of the entire r-process enhanced population of the Milky Way exists within our stellar sample, it is then concluded that core-collapse supernovae can not be the only source of r-process material.

    In an effort to confirm these numbers, we approached the calculation from a different direction. Were we to take our sample of 47 giants found in the LAMOST data, and increase it to the full estimated amount of giants in the galaxy (75,300,000), then we would expect to find 7849 enhanced giant stars, very close to the 13,060 stars from the previous calculation.

>>>>

	\begin{abstract}
		The production of heavy elements occurs through the slow and rapid neutron capture process. Numerous sites satisfy the conditions needed for the r-process but the relative frequency of these sites is unknown, largely due to the lack of a large number of stars with strong r-process signatures. Here we report the discovery of 47 r-process enhanced stars discovered in the second LAMOST data release (DR2), more than doubling the known number in the Galaxy. Taking expected rates of core-collapse supernovae and the average r-process material ejected per event, we find that core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work within the lifetime of the universe. Current estimates of neutron-star merger rates imply that there should be about 13,000 r-process enhanced stars in the Milky Way, and about $79$ in LAMOST DR2. We find that neutron-star mergers are able to create all currently known r-process enhanced stars within about 10\,Gyr. To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way. All 47 r-process enhanced stars have $[{\rm Fe/H}] > -2$, providing the first evidence against the hypothesis that r-process signatures are only found in poor metallicity environments.
	\end{abstract}

@@

    By using the assumptions listed, neutron-star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.9\times10^{9}$ years, very close to the age of the universe. From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $2.4\times10^{11}$ years, orders of magnitude longer than the age of the universe. This illustrates, with our current knowledge of core-collapse supernovae frequency, and the amount of r-process material they eject, that core-collapse supernovae cannot be the sole source of r-process enrichment in the Milky Way.

    This is reinforced by the r-process enhanced stars found in the LAMOST sample. Our 47 stars represent almost 10\% of all enhanced stars present in the Milky Way if core-collapse supernovae is considered to be the singular source of r-process enhanced stars. However, the LAMOST data release 2 only surveyed a small fraction of the Milky Way. It is highly unlikely that close to 10\% of the entire r-process enhanced population of the Milky Way exists within our stellar sample, it is then concluded that core-collapse supernovae can not be the only source of r-process material.

    In an effort to confirm these numbers, we approached the calculation from a different direction. Were we to take our sample of 47 giants found in the LAMOST data, and increase it to the full estimated amount of giants in the galaxy, then we would expect to find about 7,849 r-process enhanced giant stars, very close to the 13,060 stars from the previous calculation.
